### 2015-07-12 LOI/inc2.tex
Final committed pre-proposal with organized conflict lists.
substantial changes to intro and particularly the application use case

Our objective here is to reduce the time to knowledge, not just for a single
application, but for the entire workload in a multi-user environment, where
the storage is shared among users.
We achieve this goal by allowing selectable data quality, by trading its accuracy and error
in order to meet the time or resource constraint. 
We will explore beyond 
%the traditional high volume I/O pattern of
checkpoint/restart I/O, and will address the challenges posed by 
%other essential
key
data access patterns in the knowledge gathering process.
Ultimately, we will take the knowledge from the storage system to provide vital feedback to the middleware 
so that the best possible decisions can be autonomically made between the user intentions and
the available system resources.  
We will test our prototypes  on current and future DOE system with many of today's applications, including the
s XGC1, GTC, QMCPack, and SpecFM3D simulations.

@@

 %% Manish: Commented this since it seems to be replicated below.  
%  Our objective here is to reduce the time to knowledge, not just for a single
%application or workflow, but for the entire workload in the system. This is
%an end-to-end system wide metric relevant to the scientific discovery
%process. We will explore beyond the traditional I/O pattern of
%checkpoint/restart, and will address the challenges posed by other essential
%data access patterns in the knowledge gathering process.  Through a deeper
%insight into the scientific process we will encode and utilize accuracy and
%errors as optimization parameters.  
%Finally, we will take the knowledge from the storage system to provide vital feedback to the middleware 
%so that the best possible decisions can be autonomically  between the user intentions and
%the available system resources. Our overall goal is to ensure that optimizations can be made across
%1) a single application, 2) an ensemble of applications, and 3) the entire suite of applications which are running on the system.

@@

The success of this project will provide insights into how to build extreme scale
autonomic middleware and storage layers that can interact effectively with each
other, and bring the user in the loop through user-provided hints, allowing user 
and system knowledge to be incorporated into the SSIO software layers.
Storage resources will be managed against the needs of individual simulations 
as well as what's happening on the entire system. The impact of such a solution 
will be a significant reduction in the time to knowledge, and the overall increase in 
the effectiveness and utility of exascale simulations.

@@

  \includepdf[pages={1}]{COI/COI-all.pdf}
  \includepdf[pages={2}]{COI/COI-all.pdf}
\end{document}

>>>>

Our objective here is to reduce the time to insight, not just for a single
application, but for the entire workload in a multi-user environment, where
the storage is shared among users.
We achieve this goal by allowing selectable data quality, by trading its accuracy and error
in order to meet the time or resource constraint. 
We will explore beyond 
%the traditional high volume I/O pattern of
checkpoint/restart I/O, and will address the challenges posed by 
%other essential
key
data access patterns in the knowledge gathering process.
Ultimately, we will take the knowledge from the storage system to provide vital feedback to the middleware 
so that the best possible decisions can be autonomically made between the user intentions and
the available system resources.  
We will test our prototypes  on current and future DOE system with many of today's applications, including the
s XGC1, GTC, QMCPack, and SpecFM3D simulations.

@@

 %% Manish: Commented this since it seems to be replicated below.  
%  Our objective here is to reduce the time to insight, not just for a single
%application or workflow, but for the entire workload in the system. This is
%an end-to-end system wide metric relevant to the scientific discovery
%process. We will explore beyond the traditional I/O pattern of
%checkpoint/restart, and will address the challenges posed by other essential
%data access patterns in the knowledge gathering process.  Through a deeper
%insight into the scientific process we will encode and utilize accuracy and
%errors as optimization parameters.  
%Finally, we will take the knowledge from the storage system to provide vital feedback to the middleware 
%so that the best possible decisions can be autonomically  between the user intentions and
%the available system resources. Our overall goal is to ensure that optimizations can be made across
%1) a single application, 2) an ensemble of applications, and 3) the entire suite of applications which are running on the system.

@@

The success of this project will provide insights into how to build extreme scale
autonomic middleware and storage layers that can interact effectively with each
other, and bring the user in the loop through user-provided hints, allowing user 
and system knowledge to be incorporated into the SSIO software layers.
Storage resources will be managed against the needs of individual simulations 
as well as what's happening on the entire system. The impact of such a solution 
will be a significant reduction in the time to insight, and the overall increase in 
the effectiveness and utility of exascale simulations.

@@

  \includepdf[pages=-]{COI/COI-all.pdf}
\end{document}

### 2015-07-12 abstract.tex
substantial changes to intro and particularly the application use case

% Even with the space manipulation above, we need to cheat a little
\enlargethispage{2\baselineskip}
Scientific discovery at the exascale will not be possible without significant
new research in the management, storage and retrieval over the long lifespan
of the extreme amounts of data that will be produced.
In this project we will
demonstrate novel techniques to  facilitate efficient mapping of data
objects, even partitioning individual variables, from
the user space onto multiple storage tiers, and enable application-guided
data reductions and transformations to address capacity and bandwidth
bottlenecks. 
Our goal in this project is
to address the associated Input/Output (I/O) and storage challenges in the context of
current and emerging storage landscapes, and expedite insights into mission
critical scientific processes; which is associated with {\bf theme two} of the Funding Opportunity Announcement. To that end, we will build on the
capabilities offered by Adaptable I/O System (ADIOS) and DataSpaces at ORNL that provide I/O abstractions
and services, the Sirocco peer-to-peer file system at
Sandia, and the object storage and annotation expertise of UC Santa Cruz, to
explore application and multi-tier storage aware data management
solutions.    This project
brings together a  team with strong expertise in I/O middleware (ORNL, Rutgers), file system (SNL, UCSC) and storage (UCSC), and connects and
coordinates these key storage components in a seamless fashion.

Our objective here is to reduce the time to knowledge, not just for a single
application, but for the entire workload in a multi-user environment, where
the storage is shared among users.
We achieve this goal by allowing selectable data quality, by trading its accuracy and error
in order to meet the time or resource constraint. 
We will explore beyond 
checkpoint/restart I/O, and will address the challenges posed by 
key
data access patterns in the knowledge gathering process.
Ultimately, we will take the knowledge from the storage system to provide vital feedback to the middleware 
so that the best possible decisions can be autonomically made between the user intentions and
the available system resources.  
We will test our prototypes  on current and future Department of Energy (DOE) system with many of today's applications, including the
XGC1, GTC, QMCPack, and SpecFM3D simulations. 
Our solutions will provide  new functionalities and Application Program Interfaces (API) for:
1) specifying, at the application level, data annotations that enable the
quantification of the relative importance and utility of data objects and
enable partitioning  across the storage hierarchy;
2) specifying selectable performance/quality/cost tradeoffs from both the
application and system perspectives;
3) evaluating these tradeoffs at runtime during data placement and movement,
and executing the resultant policies in an autonomic system using models,
heuristics and continuous learning; and
4) leveraging techniques such as application-aware data compression, 
and  I/O utility to enforce these
policies.
\noindent

>>>>

% Even with the space manipulation above, we need to cheat a little
\enlargethispage{2\baselineskip}
Scientific discovery at the exascale will not be possible without significant
new research in the management, storage and retrieval over the long lifespan
of the extreme amounts of data that will be produced. Our thesis in this
project is that adding application level knowledge
about data to guide the actions of the storage system provides a substantial
benefits to the organization, storage, and access to extreme scale data,
resulting in improved productivity for computational science. 
In this project we will
demonstrate novel techniques to  facilitate efficient mapping of data
objects, even partitioning individual variables, from
the user space onto multiple storage tiers, and enable application-guided
data reductions and transformations to address capacity and bandwidth
bottlenecks. 
Our goal here is
to address the associated Input/Output (I/O) and storage challenges in the context of
current and emerging storage landscapes, and expedite insights into mission
critical scientific processes; which is associated with {\bf theme two} of the Funding Opportunity Announcement. To that end, we will build on the
capabilities offered by Adaptable I/O System (ADIOS) and DataSpaces at ORNL
and Rutgers University that provide I/O abstractions
and services, the Sirocco peer-to-peer file system at
Sandia, and the object storage and annotation expertise of UC Santa Cruz, to
explore application and multi-tier storage aware data management
solutions.    This project
brings together a  team with strong expertise in I/O middleware (ORNL, Rutgers), file system (SNL, UCSC) and storage (UCSC), and connects and
coordinates these key storage components in a seamless fashion.

We aim to reduce the time to insight, not just for a single
application, but for the entire workload in a multi-user environment, where
the storage is shared among users.
We achieve this goal by allowing selectable data quality, by trading its accuracy and error
in order to meet the time or resource constraint. 
We will explore beyond 
checkpoint/restart I/O, and will address the challenges posed by 
key
data access patterns in the knowledge gathering process.
Ultimately, we will take the knowledge from the storage system to provide vital feedback to the middleware 
so that the best possible decisions can be autonomically made between the user intentions and
the available system resources.  
We will test our prototypes  on current and future Department of Energy (DOE) system with many of today's applications, including the
XGC1, GTC, QMCPack, and SpecFM3D simulations. 
Our solutions will provide  new functionalities and Application Program Interfaces (API) for:
1) specifying, at the application level, data annotations that enable the
quantification of the relative importance and utility of data objects and
enable partitioning  across the storage hierarchy;
2) specifying selectable performance/quality/cost tradeoffs from both the
application and system perspectives;
3) evaluating these tradeoffs at runtime during data placement and movement,
and executing the resultant policies in an autonomic system using models,
heuristics and continuous learning; and
4) leveraging techniques such as application-aware data compression, 
and  I/O utility to enforce these
policies.
\noindent

### 2015-07-12 narrative/intro.tex
substantial changes to intro and particularly the application use case

{\em The purpose of computing is insight, not numbers}~\cite{Hamming:book}.
Richard Hamming's remark, made over 50 years ago at the dawning of the age of
large scale scientific computation, is even more relevant today as we prepare
for scientific simulation at exascale. 
The central objective of this proposal, ``minimizing the time to knowledge''  
with respect to scientific computing, aligns perfectly with this sentiment. 
%Hamming was a pioneer in the fields of coding theory, scientific computing and 
%information theory who would instantly sympathize with the central objective of 
%this proposal--minimizing the time to knowledge.

@@

% 
Our proposed research program is guided by the following overarching objectives:
\begin{tightItemize}
\item
{\em Address emerging storage architecture and technology landscape:}
We will address the associated I/O and storage challenges in the context of
current and emerging storage landscapes,
% and expedite insights into critical
%scientific processes, while demonstrating the validity of our approach in key
%DOE domains. 
%We will research techniques for creating and using a Scalable 
%Storage Software Infrastructure, and integrating services from the middleware 
%layer with Storage System capabilities to support 
and will develop novel strategies for distributing 
data both horizontally and vertically across the layers of these storage systems.  
Negotiation between these layers will be provided as a fundamental service, allowing users to
easily save ``the best''  data, which is automatically and appropriately placed within the
 storage stack.
\item
{\em Develop a science driven, system aware approach:}
%Our approach targets the expected characteristics of exascale storage hardware.
%The storage layer will be partitioned into multiple heterogeneous tiers with
%vastly different performance characteristics. The layers will be further
%differentiated by the constraints on capacity and data lifetime within each
%layer. Tape archival storage will still maintain data long term, but access to
%this data will be orders of magnitude slower than the next layer and naively
%accessing data from archival storage will greatly impact productivity.
%
Given that storage systems will be composed of multiple heterogeneous tiers with
vastly different performance characteristics and constraints on capacity and 
supported data lifetime, our approach will enable researchers to 
place more knowledge into the Storage Systems and Input/Output (SSIO) system 
so that data can be recast from a sequence of bytes to information rich data. This 
information rich data can then be used by the system to guide the  placement within 
the tiered storage and will optimize the time to gain knowledge and insight from 
exascale simulations.

@@

\item
{\em Emphasize impacts on science:}
%The metric we are most interested in optimizing is time to knowledge.  
%Current approaches to addressing the I/O bottleneck fall into two broad categories:
%parallel file system approaches that optimize the throughput for an entire
%system, and I/O middleware approaches that optimize the performance of a single
%application. Both approaches have been successful to date, but are unlikely to
%overcome the remaining obstacles in reaching exascale. 
Instead of trying to optimize throughput, we will seek to reduce the time to knowledge.
As extracting knowledge is the only metric that matters for scientific applications, we will
focus not only on data storage, but also on efficient retrieval of knowledge from their 
workflows.
Moreover, we aim to perform the optimization not only for a single
application, but rather for multiple workloads running on a multi-user, multi-application
system.
\end{tightItemize}

%%% Manish: I am not sure I fully understand the first part of the paragraph below.
This proposal can be summarized as research into using the varying importance of simulation data over time to
ensure that the right portions of data, with the right quality  are available to scientists when they are needed.
Application-specific information about the importance of data will be used in conjunction with system and resource-specific information
to optimize the scientists' experience in interacting with, and extracting knowledge and insight from their data.

%The overarching idea of this proposal is that data from applications can be characterized by different
%%levels of importance and different 
%levels of importance over time, which then can be used to guide the analysis and visualization later to access the most important data and deliver some level of knowledge without waiting for access to the whole original dataset. Information about the importance of the data at the application level, information about resource status and performance of the multi-level storage system, and flexible data reorganization and reduction operations at all levels can be utilized to provide a quality of service and allow users to gain insight in a timely manner.

This proposal combines knowledge and expertise 
from a wide range of sources including many leadership class applications using the Adaptable Input/Output System (ADIOS) framework,
the Sandia National Laboratory (SNL) Lightweight File Systems (LWFS) project and storage system knowledge, the metadata
management and storage systems knowledge at UCSC, and the middleware expertise
at Rutgers. We will integrate this diverse expertise to investigate how to create
a data, workflow, and application aware storage and I/O system.
%This project brings together a team with strong expertise in I/O middleware (ORNL, Rutgers),
%file system (SNL, UCSC) and storage (UCSC), and connects and
%coordinates these key storage components in a seamless fashion.
%
%\section{Scalable Storage Software Infrastructure}
%Our focus in this proposal is in Theme 2: {\em Scalable Storage Software Infrastructure} 
%We will focus on a state of the art SSIO solution to solve problems which researchers are 
%beginning to face and will make science on exascale systems
%problematic without new insights and solutions.
Our proposal will be responsive to Theme 2: {\em Scalable Storage Software Infrastructure} of the call, as summarized in Table~\ref{tab:call}.

@@

%
\paragraph{An Illustrative Example}
We use an illustrative Fusion simulation use case that our team as been working on to highlight the challenges addressed in this proposal, and to 
%The challenges addressed by this proposal are illustrated by a problem our team has been working on in the past six months. We use this motivating example to 
formulate a series of SSIO research questions that must be addressed in order to support exascale science.

The use case describes a series of XGC1~\cite{chang2006integrated} simulations that C. S. Chang (PPPL), one of the largest users of Leadership Class Facilities (over 300M hours at DOE facilities), planned to launch. These simulations were expected to produce 100~PB of data over 10 days of total runtime on the Titan system, and assembled a team of experts including the user group and I/O and storage personnel  to help ensure that the maximum amount of information would be saved. 
Due to physical resource limitations, the simulation was immediately restricted to write about 10~PB. However, when the time to write and read, together with the financial cost to archive this volume of data were fully explored, the goal was even further reduced and they would only be able to write 5~PB over the 10-day run.
%At each stage, the particular expert knowledge regarding the file system and the archival storage were not known to the user team. As these particulars were realized, significant modifications in the plans were made. Eventually, they were forced to make very hard decisions in reducing the desired 100~PB over a 10-day run to only 5~PB of data.

This forced the team to carefully scrutinize the large amount of data to be generated and save only the very most important pieces. Further, they had to divide this  reduced data into two categories: first, data they thought they would need to access while the simulation was running or shortly thereafter, and second, data they would need after the whole campaign was finished. The former category of data would be stored on disk, and the latter would be archived. Additionally, they needed to figure out how to efficiently retrieve these different categories of data for post-processing, analysis and visualization.

Finally, the team had to develop new application specific data reduction techniques and encode them into the ADIOS middleware I/O layer. In order to do this, they had to implement a rudimentary discovery system to determine which data were located on disk, and which were on tape archive.  This solution worked well for initially but after the second day significant problems occurred: I/O variability became prohibitively expensive. Although the team had reserved resources for the run, the file system was shared, and a 10X variability in I/O speeds was observed.

What is needed here is a system to monitor, predict and manage resource usage in a dynamically adaptable way. Such a system can write more data when the resource was idle, and less data when it is busy. However, the most significant problem occurs after the simulation run completes. Basic visualizations, to get a high-level view of the simulation, can take significant time due to data access latencies. While some timesteps might be on disk, others are archived on tape (where transfers could take weeks). Detailed visualization and analysis of the simulation data are even more complicated.

>>>>

{\em The purpose of computing is insight, not numbers}~\cite{Hamming:book}.
Richard Hamming's remark, made over 50 years ago at the dawning of the age of
large scale scientific computation, is even more relevant today as we prepare
for scientific simulation at exascale. 
The central objective of this proposal, ``minimizing the time to insight''  
with respect to scientific computing, aligns perfectly with this sentiment. 
%Hamming was a pioneer in the fields of coding theory, scientific computing and 
%information theory who would instantly sympathize with the central objective of 
%this proposal--minimizing the time to knowledge.

@@

% 
Our proposed research program is guided by the following overarching objectives:
\begin{tightItemize}
\item
{\em Address emerging storage architecture and technology landscape:}
We will address the associated I/O and storage challenges in the context of
current and emerging storage landscapes,
% and expedite insights into critical
%scientific processes, while demonstrating the validity of our approach in key
%DOE domains. 
%We will research techniques for creating and using a Scalable 
%Storage Software Infrastructure, and integrating services from the middleware 
%layer with Storage System capabilities to support 
and will develop novel strategies for distributing 
data both horizontally and vertically across the layers of these storage systems.  
Negotiation between these layers will be provided as a fundamental service, allowing users to
easily save ``the best''  data, which is automatically and appropriately placed within the
 storage stack.
\item
{\em Develop a science driven, system aware approach:}
%Our approach targets the expected characteristics of exascale storage hardware.
%The storage layer will be partitioned into multiple heterogeneous tiers with
%vastly different performance characteristics. The layers will be further
%differentiated by the constraints on capacity and data lifetime within each
%layer. Tape archival storage will still maintain data long term, but access to
%this data will be orders of magnitude slower than the next layer and naively
%accessing data from archival storage will greatly impact productivity.
%
Given that storage systems will be composed of multiple heterogeneous tiers with
vastly different performance characteristics and constraints on capacity and 
supported data lifetime, our approach will enable researchers to 
place more knowledge into the Storage Systems and Input/Output (SSIO) system 
so that data can be recast from a sequence of bytes to information rich data. This 
information rich data can then be used by the system to guide the  placement within 
the tiered storage and will optimize the time to gain insight from 
exascale simulations.

@@

\item
{\em Emphasize impacts on science:}
%The metric we are most interested in optimizing is time to knowledge.  
%Current approaches to addressing the I/O bottleneck fall into two broad categories:
%parallel file system approaches that optimize the throughput for an entire
%system, and I/O middleware approaches that optimize the performance of a single
%application. Both approaches have been successful to date, but are unlikely to
%overcome the remaining obstacles in reaching exascale. 
Instead of trying to optimize throughput, we will seek to reduce the time to insight.
As extracting knowledge is the only metric that matters for scientific applications, we will
focus not only on data storage, but also on efficient retrieval of knowledge from their 
workflows.
Moreover, we aim to perform the optimization not only for a single
application, but rather for multiple workloads running on a multi-user, multi-application
system.
\end{tightItemize}

%%% Manish: I am not sure I fully understand the first part of the paragraph
%%% below.
The proposed work explores how application-specific information about the
importance of data will be used in conjunction with system and
resource-specific information to optimize the scientists' experience in
interacting with, and extracting knowledge and insight from their data.
%
%The overarching idea of this proposal is that data from applications can be characterized by different
%%levels of importance and different 
%levels of importance over time, which then can be used to guide the
% analysis and visualization later to access the most important data and
% deliver some level of knowledge without waiting for access to the whole
% original dataset. Information about the importance of the data at the
% application level, information about resource status and performance of
% the multi-level storage system, and flexible data reorganization and
% reduction operations at all levels can be utilized to provide a quality of
% service and allow users to gain insight in a timely manner.
The project combines knowledge and expertise 
from a wide range of sources including many leadership class applications using the Adaptable Input/Output System (ADIOS) framework,
the Sandia National Laboratory (SNL) Lightweight File Systems (LWFS) project and storage system knowledge, the metadata
management and storage systems knowledge at UCSC, and the middleware expertise
at Rutgers. We will integrate this diverse expertise to investigate how to create
a data, workflow, and application aware storage and I/O system.
%This project brings together a team with strong expertise in I/O middleware (ORNL, Rutgers),
%file system (SNL, UCSC) and storage (UCSC), and connects and
%coordinates these key storage components in a seamless fashion.
%
%\section{Scalable Storage Software Infrastructure}
%Our focus in this proposal is in Theme 2: {\em Scalable Storage Software Infrastructure} 
%We will focus on a state of the art SSIO solution to solve problems which researchers are 
%beginning to face and will make science on exascale systems
%problematic without new insights and solutions.
Our proposal will be responsive to Theme 2: {\em Scalable Storage Software Infrastructure} of the call, as summarized in Table~\ref{tab:call}.

@@

%
\paragraph{An Illustrative Example}
We use an illustrative fusion simulation use case that our team as been working on to highlight the challenges addressed in this proposal, and to 
%The challenges addressed by this proposal are illustrated by a problem our team has been working on in the past six months. We use this motivating example to 
formulate a series of SSIO research questions that must be addressed in order to support exascale science.

The motivating use case is a series of simulations of the
ITER~\cite{dietz1996iter} fusion experiments using the
XGC1~\cite{chang2006integrated} application. XGC1 is one of the largest
applications used at the Department of Energy's (DOE's) Leadership Class
Facilities, with an allocation of over 300M hours. 
% % simulations
% % simulations planne
% %that C. S. Chang (PPPL), 
% one of the largest users of Leadership Class Facilities (LCFs) (over 300M hours at DOE facilities), planned to launch.
These simulations were expected to produce 100~PB of data over 10 days of
total runtime on the Titan system at the Oak Ridge Leadership Computing
Facility (OLCF), and required a team of experts including
the user group and I/O and storage personnel to help ensure that the maximum
amount of information would be saved. Due to physical resource limitations,
the simulation was immediately restricted to write about 10~PB. However,
when the time to write and read, together with the financial cost to archive
this volume of data was fully explored, the data size goal was further
reduced to only 5~PB over the 10 day run.

This forced a careful scrutiny of the large amount of data to be generated
and restriction of the output to only the most important pieces. Further,
this reduced data set had to be divided into two categories: first, the data
that would be accessed while the simulation was running or shortly
thereafter, and second, the data that would be needed after the whole
campaign was finished. The former category of data would be stored on disk,
and the latter would be archived. Additionally, the entire team needed to
figure out how to efficiently retrieve these different categories of data
for post-processing, analysis and visualization.

To accomplish this the application and storage teams developed new
application specific data reduction techniques and added them to the ADIOS
I/O middleware layer. A rudimentary discovery system was also created to
track what data was on disk and what was on the tape archive. Initially this
solution was sufficient, but eventually a new problem was introduced:
Although the team had reserved resources for the run, the entire file system
was shared \cite{shipman2012next} resulting in very high I/O variability
\cite{lofstead:2010:io-variability}. Addressing this variability, caused by
contention on shared resources, is an ongoing concern.

The problems faced by this user workflow motivate our research here. The use
case demonstrated the three tiers of solutions that are required -
application level knowledge of data and how it will be used, middleware
management of data and resources, and storage system level scheduling of
resources. It also provided us with new insights: First, the users and developers
of the application data can, without a great loss of encoded knowledge,
reduce the size of data that needs to be stored. Second, data storage must
be managed with input from the users to correctly decide the target of
storage operations. Third, shared resources must be managed in a way that
provides sufficient performance to all applications without encumbering the
applications with high variability in performance.

These insights drive our proposed research approach.

% Finally, the team had to develop new application specific data reduction
% techniques and encode them into the ADIOS middleware I/O layer. In order to
% do this, they  implemented a rudimentary discovery system to determine
% which data was located on disk, and which was on the tape archive. This
% solution worked well  initially but after the second day significant
% problems occurred: I/O variability became prohibitive. Although
% the team had reserved resources for the run, the file system was shared, and
% a 10X variability in I/O speeds was observed.

% What is needed here is a system to monitor, predict and manage resource
% usage in a dynamically adaptable way. Such a system can write more data when
% the resource was idle, and less data when it is busy. However, the most
% significant problem occurs after the simulation run completes. Basic
% visualizations, to get a high-level view of the simulation, can take
% significant time due to data access latencies. While some timesteps might be
% on disk, others are archived on tape (where transfers could take weeks).
% Detailed visualization and analysis of the simulation data are even more
% complicated.
